### 2009-07-22 docs/FAQ/faq.tex
made use_eos_coulomb=.true. by default in probin
made do_initial_projection a logical instead of int.

modified do_initial_projection in all inputs files
add another handy tip

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = 0
\end{verbatim}

@@

>>>>

\item {\em  How do we turn off all the initial projections to look at the
   initial velocity field as specified in initdata, instead of as
   modified by the velocity constraint?} 
%
\begin{verbatim}
    max_step  = 1
    init_iter = 0
    init_divu_iter = 0
    do_initial_projection = T
\end{verbatim}

@@

\item {\em How can I tell from a plotfile what runtime parameters were
   used for its run? or when it was created?}

   In each plotfile directory, there is a file called {\tt job\_info}
   (e.g.\ {\tt plt00000/job\_info}) that lists the build directory and
   date, as well as the value of every runtime parameter for the run.
